---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


### Loading and preprocessing the data

```{r}
unzip("activity.zip")
data <- read.csv("activity.csv")
dim(data)
str(data)
```

No post-processing currently seems necessary as items seem to be in appropropate formats.

One potential alternation would be to converte date from a factor to a date format via:
```data['date'] <- as.Date(data['date'][,], format="%Y-%m-%d")```

**Next we will explore the data with a series of questions:**  
1. What is the mean total number of steps taken per day?  
2. What is the average daily activity pattern?  
3. Imputing missing values  
4. Are there differences in activity patterns between weekdays and weekends?  

### 1: What is mean total number of steps taken per day?

```{r}
mean(data['steps'][ !is.na(data['steps'])])
```

An alternative method of calculation would be: ```mean(data['steps'][,], na.rm=TRUE)``` and also yields the same result: ```r mean(data['steps'][,], na.rm=TRUE)```

### 2: What is the average daily activity pattern?

The average daily activity pattern is calculated by summarizing the average activity per day, and then visualized via a graph, with the overall daily average, rounded to 2 decimal points, represented as a horizontal line.

The data is converted to a data.table to facilitate date grouping.

```r
library(data.table)
dt_data <- data.table(data)
averages <- dt_data[, mean(steps), by=c("date")]
overall_average <- mean(averages[['V1']], na.rm=TRUE)

plot(averages, 
    ylab="Ave. Steps",
    xlab="Date")
title("Average Steps per Day")
abline(h=overall_average, col=2)
text(-1, 30, adj=c(0,0), labels=round(overall_average,2), col=2)
```

Note: ```NA``` values are removed, by default, for the overall average and will not be graphed.


### 3: Imputing missing values


### 4: Are there differences in activity patterns between weekdays and weekends?
